---
title: "Scrollama Document with the Basic Style"
author: Yihui Xie
date: "`r Sys.Date()`"
output:
  rolldown::scrollama:
    base_format: knitr:::html_vignette
    fig_retina: 1
    fig_width: 5
    fig_height: 4
vignette: >
  %\VignetteIndexEntry{Scrollama Document with the Basic Style}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{css, example, echo=FALSE}
.level1 {
  min-height: 400px;
  border: 1px solid;
  margin-bottom: 4em;
  padding: 1em 2em 2em;
}
.is-active {
  background-color: yellow;
}
body {
  margin-bottom: 80vh;
}
```


# Setting up

A Scrollama document consists of "step elements". As you scroll down/up the document, a step element may enter or exit an offset threshold, which you can imagine as a horizontal line placed at a certain height of the viewport.

For this document, the step elements are level-one sections. Every time a level-one section enters the offset threshold, a class `is-active` is added to it. When it exits the threshold, the class is removed. To better understand the offset threshold, you can turn on the `debug` option in `rolldown::scrollama_setup()` so you can see the horizontal line:

```{r, setup, eval=FALSE, tidy=FALSE}
```

Note that `rolldown::scrollama_setup()` should be actually called _at the end_ of a document.

Below is the CSS applied to this document. Basically we added borders to level-one sections, and background colors to "active" sections.

```{css, example, eval=FALSE}
```

## Level-two heading

Level-two and below headings...

### Level-three

...are all contained in the same section.


# Text

Example text.


# Plots

You may include any number of plots in a section.

```{r}
par(mar = c(4, 4, .5, .1))
plot(pressure, type = 'h', las = 1)
```

# For experts

As mentioned in the beginning, you should call `rolldown::scrollama_setup()` at the end of a document. If you know JavaScript, you may have noticed that `scrollama_setup()` is a simple helper function to write out JavaScript like this:

```js
(function() {
  var scroller = scrollama();
  scroller.setup({"step": ".level1", "offset": 0.2})
    .onStepEnter(res => {
      res.element.classList.add("is-active");
    })
    .onStepExit(res => {
      res.element.classList.remove("is-active");
    });
  window.addEventListener("resize", scroller.resize);
})();
```

You certainly do not have to rely on this R helper function, and can write JavaScript directly in an R Markdown document. For example, if you want to use the class name `current` instead of `is-active`, you may set up Scrollama with a `js` code chunk:

````md
`r ''````{js, echo=FALSE}
(function() {
  var scroller = scrollama();
  scroller.setup({"step": ".level1", "offset": 0.2})
    .onStepEnter(res => {
      res.element.classList.add("current");
    })
    .onStepExit(res => {
      res.element.classList.remove("current");
    });
  window.addEventListener("resize", scroller.resize);
})();
```
````

For more information about Scrollama, please check out its documentation at https://github.com/russellgoldenberg/scrollama.

```{r, setup, echo=FALSE}
rolldown::scrollama_setup(
  list(step = '.level1', offset = .2, debug = TRUE)
)
```
